big stoch sim

### 2023-01-15 report/module_analysis.Rmd
Make module simulation with natural death

>>>>

# Stochastic natural death

```{r}
pq_brut <- open_dataset(here::here("res", "sim_module_d.arrow"), format = "arrow")
df <- pq_brut %>%
  collect()
colnames(df)
```

```{r}
df %>%
  filter(env_stoch == 0.5) %>%
  pivot_longer(c(stab_com, sync, avg_cv_sp), names_to = "stab", values_to =
  "values") %>%
  ggplot(aes(x = module_name, y = values, color = as.factor(alpha_ij))) +
  geom_boxplot()+
  facet_grid(
    rows = vars(stab), cols = vars(ρ),
    scales = "free_y")
```
